Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
Load tidyvers repeatedly and delete the excess
change the introduction and delete some description

Community crime has always been an inevitable challenge in the process of urban development, especially theft and assault. With the acceleration of urbanization, the increase of population density and the rise of resource demand, the complexity of crime patterns has also increased. Understanding how crime in different communities changes over time and space becomes critical to the problem of building safe communities. Research shows that urban growth often leads to a non-linear increase in crime rate. @bettencourt2007growth also mentioned that communities with larger populations usually experience higher crime rates. This paper mainly analyzes the data of theft and assault rates of each community from 2014 to 2023. To explore the differences in size and crime rates in different communities and the accompanying time fluctuations.

This article focuses on two key aspects of crime data. First, by analyzing trends in theft rates between 2014 and 2023, significant differences were found across communities.Through data analysis in this paper and @oliveira2021more argue that some communities experienced high rates of burglary during the decade, while others experienced relatively flat or small fluctuations in crime. In addition, the burglary rate is analyzed using a boxplot to show the distribution of crime rates over time, revealing which areas have consistently high or fluctuated crime rates. The analysis found that the increase in theft rates in some areas from 2019 May have been influenced by different economic and social conditions at the time: By @syamsuddin2021effect, starting in 2019, the global COVID-19 pandemic forced people to work and study from home, and some people lost their source of income.

Second, the relationship between population size and assault rates in 2019 suggests that communities with larger populations generally have higher crime rates. According to the @bettencourt2007growth, this verifies the city size effect theory, that is, the expansion of city size may lead to higher social interaction and crime rate. However, the fact that some areas with small population have higher assault rate also indicates that crime rate is also affected by unexpected factors other than population size. By using a bar chart to compare the attack rates of each community in 2023, it is shown that some high-traffic communities have significantly higher attack rates than others.This confirms the crime opportunity theory from @oliveira2021more, which states that more densely populated areas have more crime opportunities.

Through the analysis of these aspects, the time and space dimension of crime are discussed in detail. Through a comprehensive analysis of crime dynamics from different aspects of the data, the burglary rate can reflect the economic state of the community, while the assault crime is often related to social tensions and community security. This paper aims to explore these two categories of crime in depth, assessing how they are evolving in the context of a growing urban population. Finally, the conclusion of the study is to propose targeted management intervention measures to relevant judicial departments and law enforcement agencies and how to effectively carry out crime prevention, such as resource redistribution.

@@

# Graph

## Graph 1

@@

#### First Graph ####
library(tidyverse)
# This code is based on sample from ChatGPT

@@

### Graph 1 Analyse

@@

## Graph 2

@@

### Graph 2 Analyse

@@

## Graph 3

@@

### Graph 3 Analyse

@@

## Graph 4

@@

### Graph 4 Analyse

@@

# Discussion

@@

## First discussion point {#sec-first-point}

>>>>

Between 2014 and 2023, as urbanization accelerates, the crime dynamics in Toronto change significantly. Crime is concentrated in certain neighborhoods, such as those with poor socioeconomic conditions, where residents tend to face a higher risk of property and violence [@wang2019spatial]. Since 2020, the Covid-19 outbreak has intensified this trend. [@syamsuddin2021effect] noted a spike in thefts in many cities around the world during the pandemic, due to socio-economic instability and reduced social activity caused by lockdowns. Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods. In addition, population growth also increases the chance of crime, and the chance of crime is higher in areas with higher population density and resource shortage [@bettencourt2007growth].

Data on Neighbourhood Crime Rates were obtained, as described in @sec-data-overview. This paper mainly analyzes the burglary and assault rates in each community from 2014 to 2023, exploring the differences in community size and crime rates and the accompanying time fluctuations. The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates). By assessing these dynamics, we hope to inform crime prevention and resource allocation in Toronto, particularly in high-risk neighbourhoods where there is a long-term need for more police and social resources.

The structure of this paper is as follows: {#sec-data-overview} presents the data sources and methodology, {#sec-data-overview} presents the results of the analysis, and {#sec-discussion} discusses the policy implications of the findings, particularly with regard to how to respond to crime hotspots in Toronto.

@@

@@

#### First Graph ####
# This code is based on sample from ChatGPT

@@

@@

@@

@@

@@

@@

@@

@@

# Discussion {#sec-discussion}

@@

## First discussion point
